Conjure: Summoning Proxies from Unused Address Space

### 2019-09-28 paper/figures.tex
Cleanup in progress

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-flow2.png}
    \caption{\textbf{\scheme Operations}\,---\,\rm%
        A \scheme session is constructed in two pieces. First a client registers by sending a TLS connection
        to the decoy host (see Figure 2c) with a steganographically tagged payload.
        This registration contains the true ``covert'' address that the client would like to connect to and a seed 
        which the \scheme station uses to derive the Phantom IP address for the session (green dashed flow). 
        Second, the client derives the same 
        Phantom IP address and connects directly to it using the proxy protocol (e.g. OSSH) specified in
        the registration (purple dotted flow). The station identifies registered packets by source IP, destination IP,
        and destination port (client IP, phantom IP and port respectively). The traffic is passed 
        to a proxy server handling the specific proxy protocol, which ultimately proxies traffic to
        the covert address.
        \\\hspace{\textwidth}
        Secrets for the individual application proxy service are shared out of band or derived from the secret seed shared
        between client and station during registration, preventing an adversary from being
        able to successfully connect to the application in follow up probes.
    }
    \label{fig:overview}
\end{figure}
}

\newcommand{\FigHighLevel}{
\begin{figure}[]
    \centering
    %\vspace{-0.54in}
    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
    \caption{\textbf{\scheme Overview}\,---\,\rm%
      An ISP deploys a \scheme station, which sees a passive tap of passing traffic.
      Following a steganographic registration process, a client can connect
      to an unused IP address in the ISP's AS, and the station will
      inject packets to communicate with the client as if there were a proxy server at that address.
    }
    \label{fig:highlevel}
\end{figure}
}

@@

\newcommand{\TabApplications}{
\begin{table}[t]
    \centering
    \begin{tabular}{l|ccccc}
            & \rot{OSSH~\cite{ossh}} &
              \rot{\texttt{obfs4}~\cite{obfs4}} &
              \rot{Mask Sites} &
              \rot{TLS eSNI} & \rot{WebRTC} \\
            \hline
            Active probe resistant  & \yes  & \yes & \yes & \yes & \yes \\
            Randomized or Tunneling & R    & R    & T    &  T   & T \\
            Known passive attack    & \cite{Fifield2017a} & \cite{wang2015seeing} & - & - & - \\
            \scheme implementation  & \yes & \no  & \yes  & \no & \no \\
    \end{tabular}
    \medskip
    \caption{\textbf{\scheme Applications}\,---\,\rm%
    ``Active probe resistant`` protocols are designed to look innocuous even if scanned by a censor.
    ``Tunneling`` (T) protocols use another protocol (e.g. TLS) to blend in, while ``Randomized`` (R)
        ones attempt to have no discernable protocol fingerprint or headers.
        For existing protocols, we list any known attacks suggested in the literature that let censors
        passively detect them. We also list if we have implemented the application in our prototype.}
    \label{tab:applications}
\end{table}
}

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/dark-decoy-impl1.png}
    \caption{\textbf{Station Architecture}\,---\,\rm%
        We used PF\_RING to receive packets from a 20~Gbps tap which we load balance
        across 4~CPU cores. The detector processes identify registrations, sending notification to
        all other cores via redis and to the local application 
        via ZMQ when a new registration is received . The detector also
        identifies packets associated with registered flows and diverts them
        to the local application which handles proxying connections. The local 
        application determines which transport the flow should use based on a parameter specified in
        the client's registration and initializes a goroutine to handle forwarding. 
        \\\hspace{\textwidth}
        A censor trying to interfere in this
        connection would need to take over the clients IP address in a precise window (after the 
        registration but before the client connects to the phantom) and correctly guess the phantom host's 
        IP address (or connect to all possible phantom IPs) before the active probe traffic gets to the local application. 
        At this point their connection will fail in a manner specific to the transport that the client specified
        in the registration (e.g. connecting to OSSH without knowledge of the pre-shared secret).}
    \label{fig:implementation}
\end{figure}
}

\newcommand{\FigEvolution}{
\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figures/refraction-v1}
    \vspace{-3pt}

    \caption{\textbf{First generation systems}\rm\ for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows. ISPs worried that if the inline element failed, it could bring down the network.\looseness=-1}
    \label{fig:refraction-v1}
  \end{subfigure}
  \vspace{16pt}

  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figures/tapdance}
    \vspace{-3pt}

    \caption{\textbf{TapDance}\rm\ is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets. TapDance has recently been deployed at a mid-size ISP, but the techniques used to silence the decoy site and participate in the client--decoy TCP connection mid-stream add significant complexity, performance bottlenecks, and detection risk.}
    \label{fig:tapdance}
  \end{subfigure}
  \vspace{16pt}

  \begin{subfigure}{\columnwidth}
    \label{fig:evolutionconjure}
    \includegraphics[width=\columnwidth]{figures/dark-decoys}
    \vspace{-3pt}

    \caption{\textbf{\scheme}\rm, our third-generation Refraction Networking design, overcomes these limitations.  It uses two sessions. First, the client connects to a decoy site and embeds a steganographic registration message, which the station receives using only a passive tap.  Second, the client connects to a ``phantom host'' where there is no running server, and the station proxies the connection in its entirety.}
    \label{fig:dark-decoys}
  \end{subfigure}

  \vspace{12pt}
  \caption{\textbf{Evolution of Refraction Networking}}
\end{figure}
}

>>>>

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-flow2.png}
    \caption{\textbf{\scheme Operations}\,---\,\rm%
        A \scheme session is constructed in two pieces. First a client registers by sending a TLS connection
        to the decoy host (see Figure 2c) with a steganographically tagged payload.
        This registration contains the true ``covert'' address that the client would like to connect to and a seed 
        which the \scheme station uses to derive the Phantom IP address for the session (green dashed flow). 
        Second, the client derives the same 
        Phantom IP address and connects directly to it using the proxy protocol (e.g. OSSH) specified in
        the registration (purple dotted flow). The station identifies registered packets by source IP, destination IP,
        and destination port (client IP, phantom IP and port respectively). The traffic is passed 
        to a proxy server handling the specific proxy protocol, which ultimately proxies traffic to
        the covert address.
        Secrets for the individual application proxy service are shared out of band or derived from the secret seed shared
        between client and station during registration, preventing an adversary from 
        successfully connecting to the application in follow up probes.
    }
    \label{fig:overview}
\end{figure}
}

\newcommand{\FigHighLevel}{
\begin{figure}[]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
    \caption{\textbf{\scheme Overview}\,---\,\rm%
      An ISP deploys a \scheme station, which sees a passive tap of passing traffic.
      Following a steganographic registration process, a client can connect
      to an unused IP address in the ISP's AS, and the station will
      inject packets to communicate with the client as if there were a proxy server at that address.
    }
    \label{fig:highlevel}
\end{figure}
}

@@

\newcommand{\TabApplications}{
\begin{table}[t]
    \centering
    \begin{tabular}{lccccc}
            & \rot{OSSH~\cite{ossh}} &
              \rot{\texttt{obfs4}~\cite{obfs4}} &
              \rot{Mask Sites} &
              \rot{TLS eSNI} & \rot{WebRTC} \\
            \toprule
            Active probe resistant  & \yes  & \yes & \yes & \yes & \yes \\
            Randomized or Tunneling & R    & R    & T    &  T   & T \\
            Known passive attack    & \cite{Fifield2017a} & \cite{wang2015seeing} & - & - & - \\
            \scheme implementation  & \yes & \no  & \yes  & \no & \no \\
            \bottomrule
    \end{tabular}
    \medskip
    \caption{\textbf{\scheme Applications}\,---\,\rm%
    ``Active probe resistant'' protocols are designed to look innocuous even if scanned by a censor.
    ``Tunneling'' (T) protocols use another protocol (e.g. TLS) to blend in, while ``Randomized'' (R)
        ones attempt to have no discernable protocol fingerprint or headers.
        For existing protocols, we list any known attacks suggested in the literature that let censors
        passively detect them. We also list if we have implemented the application in our prototype.}
    \label{tab:applications}
\end{table}
}

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/dark-decoy-impl1.png}
    \caption{\textbf{Station Architecture}\,---\,\rm%
        We used PF\_RING to receive packets from a 20~Gbps tap which we load balance
        across 4~CPU cores. The detector processes identify registrations, sending notification to
        all other cores via redis and to the local application 
        via ZMQ when a new registration is received. The detector also
        identifies packets associated with registered flows and diverts them
        to the local application which handles proxying connections. The local 
        application determines which transport the flow should use based on a parameter specified in
        the client's registration and initializes a goroutine to handle forwarding. 
        A censor trying to interfere in this
        connection would need to take over the clients IP address in a precise window (after the 
        registration but before the client connects to the phantom) and correctly guess the phantom host's 
        IP address (or connect to all possible phantom IPs) before the active probe traffic gets to the local application. 
        At this point their connection will fail in a manner specific to the transport that the client specified
        in the registration (e.g. connecting to OSSH without knowledge of the pre-shared secret).}
    \label{fig:implementation}
\end{figure}
}

\newcommand{\FigEvolution}{
\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figures/refraction-v1}

    \caption{\textbf{First generation systems}\rm\ for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows. ISPs worried that if the inline element failed, it could bring down the network.\looseness=-1}
    \label{fig:refraction-v1}
  \end{subfigure}
  \vspace{12pt}

  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figures/tapdance}

    \caption{\textbf{TapDance}\rm\ is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets. TapDance has recently been deployed at a mid-size ISP, but the techniques used to silence the decoy site and participate in the client--decoy TCP connection mid-stream add significant complexity, performance bottlenecks, and detection risk.}
    \label{fig:tapdance}
  \end{subfigure}
  \vspace{12pt}

  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figures/dark-decoys}

    \caption{\textbf{\scheme}\rm, our third-generation Refraction Networking design, overcomes these limitations.  It uses two sessions. First, the client connects to a decoy site and embeds a steganographic registration message, which the station receives using only a passive tap.  Second, the client connects to a ``phantom host'' where there is no running server, and the station proxies the connection in its entirety.}
    \label{fig:evolutionconjure}
    \label{fig:dark-decoys}
  \end{subfigure}
  \caption{\textbf{Evolution of Refraction Networking}}
\end{figure}
}

### 2019-09-28 paper/paper.tex
Cleanup in progress

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{dblfloatfix} % magic
\usepackage{balance}
\usepackage{paralist}
\usepackage{wasysym}
\usepackage{xparse}
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\urlstyle{rm}

@@

Over half of Internet users globally
now live in countries that block political, social, or religious content
online~\cite{fotn2018}.
%Existing circumvention strategies on shaky ground
%-domain fronting going away
%-active probing of existing proxies
%-Cenosrs fingerprinting known protocols
Meanwhile, many popular tools and techniques for circumventing such censorship
have ceased to function, because censors have evolved new ways to block them~\cite{ensafi-tor,great-cannon}
or infrastructure they rely on has become unavailable.

@@

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
A family of techniques called Refraction Networking~\cite{telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
as Decoy Routing, has made promising steps towards that goal.
These techniques operate in the network's core, at cooperating Internet Service Providers
(ISPs) outside censoring countries~\cite{refraction-site}.  Clients access circumvention services by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.  Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction Networking is widely deployed~\cite{robinson2013collateral}.

@@

TapDance was designed for ease of deployment.
Instead of in-line network devices required by earlier schemes, it
calls for only a passive tap.
This ``on-the-side'' approach, though much friendlier from an ISP's
perspective, leads to major challenges when interposing in an ongoing
client-to--decoy connection:
\begin{compactitem}
\item Implementation is complex and error-prone, requiring kernel
  patches or a custom TCP stack.
\item To avoid detection, the system must carefully mimic
  subtle features of each decoy's TCP and TLS behavior.
\item The architecture cannot resist active probing attacks, where the
  censor sends specially crafted packets to determine whether a
  suspected connection is using TapDance.
\item Interactions with the decoy's network stack limit the length and
  duration of each connection, forcing TapDance to multiplex
  long-lived proxy connections over many shorter decoy
  connections. This adds overhead and creates a traffic pattern
  that is challenging to conceal.
\end{compactitem}

@@

\smallskip

In this paper, we present \textbf{\scheme}, a Refraction
Networking protocol that overcomes these challenges while retaining
TapDance's ISP-friendly deployment requirements\footnote{
We have released the open source implementation of the Conjure client at 
\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.}.
Our key innovation is an architecture that avoids
having to actively participate in client-to-decoy connections.

@@

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from phantom
hosts.
Furthermore, we assume
asymmetric routing (i.e. that the tap might only see packets from but not to the
client).
However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.

@@

We allow the censor access to the client to register and use its own phantom hosts, 
so the system should ensure that these will not reveal the phantom hosts of other users. The
censor can also actively probe addresses that it sees users accessing, and can
employ tools such as ZMap~\cite{zmap13} to scan large network blocks, excepting
large IPv6 prefixes (e.g. a /32 IPv6 prefix contains $2^{96}$ addresses).

@@

\medskip

@@

\subsection{Transports}

@@

\paragraph{Encrypted SNI}
\label{esni}

TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
\scheme transport design. For instance, TLS~1.3 handshakes include encrypted
certificates, removing a strong traffic classification feature.
Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
Hello, meaning we would have to choose a realistic domain to fool a censor.

@@

\paragraph{Mask Sites}
\label{sec:mask-sites}

Another option to overcome active and passive probing attacks is to mimic existing TLS sites.
In this application, we simply forward traffic between any connecting clients
and a real TLS site. To a censor, our phantom site
will be difficult to distinguish from the actual ``mask'' site, making it expensive for
them to block without potentially blocking the real site. TLS connections to the
\scheme station will terminate exactly as connections to the mask site would, with
\scheme acting as a transparent TCP-layer proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-side shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

@@

\paragraph{Mask Site Selection}

Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a phantom host in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a phantom host at an IP address pretends to be a domain that
globally resolves to a single (different) IP address, the censor could also trivially
identify and block the phantom host.

\textit{Nearby sites ---} pick websites that are
legitimately hosted in or near the network of the phantom host addresses
effectively creating copies of legitimate sites. However, other signals such as 
DNS may reveal the true mask site.

\textit{Popular sites ---} choose mask sites from a list such as the Alexa
top site~\cite{alexa-top500} list. Although it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own data centers and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

\textit{Passive observation ---} collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by at the network tap. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the phantom host addresses
that pass by the tap.

@@

We implemented \scheme and deployed a station at a mid-sized transit ISP tapping 
traffic from a 20~Gbps router. We used PF\_RING to
consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. Once a registration 
is detected the local application is notified via an 
out-of-band ZMQ~\cite{zmq} connection, which provides the
registering client's IP address, the seed, and other configuration
information. We note that this is not along a critical timing path for 
proxying connections and no client packets are sent over ZMQ.

The detectors forwards all packets destined for a (registered) phantom host address to the local
\textbf{application} via tun interfaces and \texttt{iptables} DNAT rules that rewrite the destination IP,
allowing the local application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

@@

% Our detector is a modified fork of the open source TapDance
% implementation~\cite{tapdance-source}.
We implemented our detector in approximately 1,800 lines of Rust (compared to
over 5,000 lines for TapDance)\footnote{excluding (from both) about 3,000 lines
of auto-generated protobuf code}.

@@

\subsection{Application \& Transports}

@@

To measure and quantify this problem, we collected and analyzed 16 hours of
netflow data at our ISP tap. We extracted 4013 IPv6 addresses observed in the /32
IPv6 prefix routed by the ISP (out of 32,817 total observed). To confirm the
hypothesis that 0 bits are more common in IPv6 addresses, we counted the number
of bits set in each address. Figure~\ref{fig:ipbits} shows a histogram of the
number of bits set and compares it to the histogram of a uniformly random set of
addresses.\footnote{The random distribution's center is skewed from 64 due to
the number of set bits in our fixed /32 network prefix.} Although these
distributions are distinguishable, they do have significant overlap. Given
enough samples, a censor could trivially tell if the addresses were chosen
randomly or were legitimate hosts. However, a censor's job is significantly
harder, and they must tell from a single sample which distribution it comes
from. The presence of random-looking addresses makes it difficult for censors to
block such hosts outright.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{dblfloatfix} % magic
\usepackage{balance}
%\usepackage{paralist}
\usepackage{wasysym}
\usepackage{xparse}
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\urlstyle{rm}

@@

Over half of Internet users globally
now live in countries that block political, social, or religious content
online~\cite{fotn2018}.
%Existing circumvention strategies on shaky ground
%-domain fronting going away
%-active probing of existing proxies
%-Cenosrs fingerprinting known protocols
Meanwhile, many popular tools and techniques for circumventing such censorship
become ineffective, because censors have evolved new ways to block them~\cite{ensafi-tor,great-cannon}
or infrastructure they rely on has become unavailable.

@@

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
A family of techniques called Refraction Networking~\cite{telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
as Decoy Routing, has made promising steps towards that goal.
These techniques operate in the network's core, at cooperating Internet Service Providers
(ISPs) outside censoring countries~\cite{refraction-site}.  Clients access circumvention services by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.  Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction Networking is widely deployed~\cite{robinson2013collateral}.
\looseness=-1

@@

TapDance was designed for ease of deployment.
Instead of in-line network devices required by earlier schemes, it
calls for only a passive tap.
This ``on-the-side'' approach, though much friendlier from an ISP's
perspective, leads to major challenges when interposing in an ongoing
client-to-decoy connection:

\begin{itemize}
\item Implementation is complex and error-prone, requiring kernel
  patches or a custom TCP stack.
\item To avoid detection, the system must carefully mimic
  subtle features of each decoy's TCP and TLS behavior.
\item The architecture cannot resist active probing attacks, where the
  censor sends specially crafted packets to determine whether a
  suspected connection is using TapDance.
\item Interactions with the decoy's network stack limit the length and
  duration of each connection, forcing TapDance to multiplex
  long-lived proxy connections over many shorter decoy
  connections. This adds overhead and creates a traffic pattern
  that is challenging to conceal.
\end{itemize}

@@

\smallskip
\noindent\textbf{Conjure}\enskip
In this paper, we present \scheme, a Refraction
Networking protocol that overcomes these challenges while retaining
TapDance's ISP-friendly deployment requirements\footnote{
We have released the open source implementation of the Conjure client at 
\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.}.
Our key innovation is an architecture that avoids
having to actively participate in client-to-decoy connections.

@@

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from phantom
hosts.
Furthermore, we assume
asymmetric routing (i.e. that the tap might only see packets from but not to the
client).
However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.
\looseness=1

@@

We allow the censor access to the client to register and use its own phantom hosts, 
so the system should ensure that these will not reveal the phantom hosts of other users. The
censor can also actively probe addresses that it sees users accessing, and can
employ tools such as ZMap~\cite{zmap13} to scan large network blocks, excepting
large IPv6 prefixes (e.g. a /32 IPv6 prefix contains $2^{96}$ addresses).
\looseness=1

@@

@@

\subsection{Transports}
%\TODO{The organization of this into subsubsections and paragraphs is a mess.  Can we flatten it a bit or divide into two sections?}

@@

\paragraph{Encrypted SNI}\label{esni}
TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
\scheme transport design. For instance, TLS~1.3 handshakes include encrypted
certificates, removing a strong traffic classification feature.
Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
Hello, meaning we would have to choose a realistic domain to fool a censor.

@@

\paragraph{Mask Sites}\label{sec:mask-sites}
Another option to overcome active and passive probing attacks is to mimic existing TLS sites.
In this application, we simply forward traffic between any connecting clients
and a real TLS site. To a censor, our phantom site
will be difficult to distinguish from the actual ``mask'' site, making it expensive for
them to block without potentially blocking the real site. TLS connections to the
\scheme station will terminate exactly as connections to the mask site would, with
\scheme acting as a transparent TCP-layer proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-side shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

@@

\paragraph{Mask Site Selection}
Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a phantom host in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a phantom host at an IP address pretends to be a domain that
globally resolves to a single (different) IP address, the censor could also trivially
identify and block the phantom host.
Several approaches are possible:

\begin{description}
\item[\rm\em Nearby sites:] pick websites that are
legitimately hosted in or near the network of the phantom host addresses
effectively creating copies of legitimate sites. However, other signals such as 
DNS may reveal the true mask site.

\item[\rm\em Popular sites:] choose mask sites from a list such as the Alexa
top site~\cite{alexa-top500} list. Although it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own data centers and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

\item[\rm\em Passive observation:] collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by at the network tap. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the phantom host addresses
that pass by the tap.

\end{description}

@@

We implemented \scheme and deployed a station at a mid-sized transit ISP tapping 
traffic from a 20~Gbps router. We used PF\_RING to
consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. Once a registration 
is detected the local application is notified via an 
out-of-band ZMQ~\cite{zmq} connection, which provides the
registering client's IP address, the seed, and other configuration
information. We note that this is not along a critical timing path for 
proxying connections and no client packets are sent over ZMQ\@.

The detectors forwards all packets destined for a (registered) phantom host address to the local
\textbf{application} via tun interfaces and \texttt{iptables} DNAT rules that rewrite the destination IP,
allowing the local application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe in the following subsections.
% Along with the client?

@@

% Our detector is a modified fork of the open source TapDance
% implementation~\cite{tapdance-source}.
We implemented our detector in approximately 1,800 lines of Rust, compared to
over 5,000 lines for TapDance (excluding from both auto-generated protobuf code).

@@

\subsection{Application and Transports}

@@

To measure and quantify this problem, we collected and analyzed 16 hours of
netflow data at our ISP tap. We extracted 4013 IPv6 addresses observed in the /32
IPv6 prefix routed by the ISP (out of 32,817 total observed). To confirm the
hypothesis that 0 bits are more common in IPv6 addresses, we counted the number
of bits set in each address. Figure~\ref{fig:ipbits} shows a histogram of the
number of bits set and compares it to the histogram of a uniformly random set of
addresses. (The random distribution's center is skewed from 64 due to
the number of set bits in our fixed /32 network prefix.) Although these
distributions are distinguishable, they do have significant overlap. Given
enough samples, a censor could trivially tell if the addresses were chosen
randomly or were legitimate hosts. However, a censor's job is significantly
harder, and they must tell from a single sample which distribution it comes
from. The presence of random-looking addresses makes it difficult for censors to
block such hosts outright.
